Design Reinforcement of Structures (DRB) is an open-source, free web-based software, developed by students of 
Testing and Consultancy Cell (TCC), under the guidance of Dr. H.S. Rai. This software is used to gives the 
Different views of structure of a building like Beams and Columns used to make a structure. This software can be used by Civil Engineers to view and anaylsis the strucure.

 The main task of this application is to get data as input from user and then it can compute 
the result and draw 2D views of the structure and user can download the views as a pdf format .
This software is structured by keeping in view that user of this software can be both 
a Civil Engineer or a simple man whose job is just to enter data to software 
in order that an engineer can analyze later from the result stability of the structure.
This software also provides the intermediate values for engineering student 
to deeply analyze the process of computation to be done in order to get output values.


The core part of DRB is implemented using JavaScript for processing, canvas for graphics and  jspdf.js for output file (PDF) generation, Angular.js 
for web interface. To provide the User Experience to the users, 
CSS and Bootstrap has been used.


My training being not based on particular language or technology, different type of open-source softwares and technologies are 
used in this project and many during my training which are not used in this 
project like Angular.js (for a declarative user interface and as front-end), Node.js (for server-side and managing databases).
